Machine learning high multiplicity matrix elements for electron-positron and hadron-hadron colliders

### 2023-03-13 paper2.tex
chapter 6 typo
mu_{R} range typo

This informs our ansatz for the k-factor, which can is given as
\begin{equation}
    k_{n+1} = C_{0} + \sum_{\{ijk\}} C_{ijk}\dfrac{X_{ijk}^{1,F}}{X_{ijk}^{0}} \,
    \label{eq:1L_ansatz}
\end{equation}
where $C_{0}$ and $C_{ijk}$ are coefficients fitted by the neural network.
$C_{0}$ is an additive term aiming to model the reduced
k-factor, and $C_{ijk}$ are multiplying the ratio of
antenna functions to fit the single collinear, and
soft limits in multiple regions of phase-space.
The sum over $\{ijk\}$ denotes the sum over
the relevant permutations of final-state partons, accounting
for all the relevant singular limits of the k-factor.
This sum allows the neural network to make use of all
the provided antenna functions to make an approximation
of the colour-summed matrix element.
The full set of antenna functions which we implement into our
model is detailed below.

@@

For each phase-space point generated, we sample a
renormalisation scale, $\log(\mu_{R})$, from a uniform distribution
with end points at $[\log(s_{\mathrm{com}}/4), \log(4s_{\mathrm{com}})]$.
In other words, we sample the renormalisation scale logarithmically.
We observe that the neural network manages to learn the
renormalisation scale dependence well therefore opt to
sample $\mu_{R}$ in a wider range than is usually used
for the conventional scale variations which varies $\mu_{R}$
up and down by factors 2.

>>>>

This informs our ansatz for the k-factor, which is given as
\begin{equation}
    k_{n+1} = C_{0} + \sum_{\{ijk\}} C_{ijk}\dfrac{X_{ijk}^{1,F}}{X_{ijk}^{0}} \,
    \label{eq:1L_ansatz}
\end{equation}
where $C_{0}$ and $C_{ijk}$ are coefficients fitted by the neural network.
$C_{0}$ is an additive term aiming to model the reduced
k-factor, and $C_{ijk}$ are multiplying the ratio of
antenna functions to fit the single collinear, and
soft limits in multiple regions of phase-space.
The sum over $\{ijk\}$ denotes the sum over
the relevant permutations of final-state partons, accounting
for all the relevant singular limits of the k-factor.
This sum allows the neural network to make use of all
the provided antenna functions to make an approximation
of the colour-summed matrix element.
The full set of antenna functions which we implement into our
model is detailed below.

@@

For each phase-space point generated, we sample a
renormalisation scale, $\log(\mu_{R})$, from a uniform distribution
with end points at [$\log(\sqrt{s_{\text{com}}}/4)$, $\log(4\sqrt{s_{\text{com}}})$].
In other words, we sample the renormalisation scale logarithmically.
We observe that the neural network manages to learn the
renormalisation scale dependence well therefore opt to
sample $\mu_{R}$ in a wider range than is usually used
for the conventional scale variations which varies $\mu_{R}$
up and down by factors 2.
